---
output:
  word_document: default
  html_document: default
---
# BAN 502 - Refresher Assignment
## Tate, Levi

```{r task 1 & 2}
library(tidyverse)
diamonddata = diamonds
```

```{r task 3}
ggplot(diamonddata, aes(x = carat, y = price)) +
  geom_point()
```
Generally, as carat size increases, price increases for diamonds.

```{r task 4}
ggplot(diamonddata, aes(x = carat, y = price, color = cut)) +
  geom_point()
```
As carat increases, cut quality decreases and price increases. 

```{r task 5}
ggplot(diamonddata, aes(x = carat, y = price, color = cut)) +
  geom_point() +
  facet_wrap(~ color)
```
As color moves from D to J, there is more variability in carat size(more diamonds in color J have a greater carat). Cut quality and price exponentially increase in color D diamonds and slowly steadies out as color changes(D to J). 

```{r task 6}
inventory <- read_csv("InventoryData.csv")
summary(inventory)
```
```{r task 7}
inventoryA <- inventory %>% 
                      filter(Supplier == "A")
```

After filtering the inventory to supplier A only, there  are 3695 rows in the new data frame.

```{r task 8}
inventoryA = mutate(inventoryA, OnHandRatio = `On Hand` / `Annual Demand`)
```

The code above mutates the data frame inventoryA by adding a new column, OnHandRatio, which provides the ratio of On Hand and Annual Demand.

```{r task 9}
avg_cost <- inventoryA %>%
                      group_by(`Item SKU`) %>%
                      summarize(SKUAvgCost = mean(`Cost per Unit ($)`))
```

Given your previous course experience with R/RStudio, what topics/concepts did you find to be most challenging? \

In module 6 of MIS 503, working with dates was the most challenging topic/concept. 

