---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Module 2 - BAN 502
## Tate, Levi
### Simple Linear Regression and Correlation

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
```

```{r}
air = airquality
```

The air data frame has 6 variables with 153 observations. Ozone and Solar.R are\ missing some observations. The variable Ozone is likely to be the response variable.

```{r}
air2 <- drop_na(air)
```

After deleting the missing observations, 6 columns and 111 rows remain.

```{r}
ggpairs(air2)

ggcorr(air2, label = TRUE)
```
Temperature is the most strongly correlated with Ozone: ~.7
Day is is the least strongly correlated with Ozone: -.005

```{r}
ggplot(air2, aes(x = Temp, y = Ozone)) +
geom_point(alpha = 0.5) +
  theme_bw()
```

```{r}
Ozone_temp_simple = recipe(Ozone ~ Temp, air2)

lm_model =
  linear_reg() %>%
  set_engine("lm")

lm_wflow =
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(Ozone_temp_simple)

lm_fit = fit(lm_wflow, air2)
```

```{r}
summary(lm_fit$fit$fit$fit)
confint(lm_fit$fit$fit$fit) # 1.96-2.91
```

Adjusted R-squared: .4833 | predictor variable is significant: < 2e-16

```{r}
ggplot(air2, aes(x = Temp, y = Ozone)) +
geom_point() +
geom_smooth(method = "lm", se =FALSE, color = "red") +
  theme_bw()
```

```{r}
testdata = data.frame(Temp = 80)
predict(lm_fit, new_data = testdata)

-147.6461 + 2.4391*80
```

**Assumption 1:** The predictor and the response variable have a linear relationship
True, although the R sqaured value isn't great. should compare to other models

**Assumption 2:** Model errors (residuals) are independent
Use the Durbin-Watson Test to examine independence of residuals.

```{r}
dwtest(lm_fit$fit$fit$fit)
```
DW = 1.8644, p-value = .2123: slight positive autocorrelation. fail to reject null hypothesis with this p-value. residuals are likely independent.

**Assumption 3:** Model residuals exhibit constant variance
Examine a plot of variables

```{r}
air2 = air2 %>% mutate(resid1 = lm_fit$fit$fit$fit$residuals)
ggplot(air2, aes(x = Temp, y = resid1)) +
  geom_point() +
  theme_bw()
```
A non linear effect is present.

**Assumption 4:** Model Residuals are normally distributed
Examine a histogram of the residuals

```{r}
ggplot(air2, aes(x = resid1)) +
  geom_histogram() +
  theme_bw()
```
the residuals histogram is slightly skewed and moderately normally distributed.


